---
title: "Untitled"
output: html_document
date: "2023-03-06"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(data.table)

geography<-read.csv("West_Mids_unique_geography.csv")
postcodes<-read.csv("West_Mids_Postcodes_10km_buffer.csv") 
acute<-read.csv("acuteproviders_geography.csv")
cdc<-read.csv("CDC_geography.csv")

#Travel time data to CDCs
car_cdc <- fread("car_cdc.csv")%>%
    filter(OriginId!="OriginId")%>%
mutate_at(1:4, as.numeric)%>%
distinct(OriginId, DestinationId, .keep_all = TRUE)
PT_cdc <- fread("PT_cdc.csv")%>%
        filter(OriginId!="OriginId")%>%
mutate_at(1:3, as.numeric)%>%
distinct(OriginId, DestinationId, .keep_all = TRUE)

#Travel time data to Acute Providers
car_acute <- fread("tracc/car_acute.csv")


#PT calculation for acute providers needed to be done is 6 parts
PT_acute_ori1_des1<-fread("tracc/PT_acute_ori1_des1.csv")
PT_acute_ori2_des1<-fread("tracc/PT_acute_ori2_des1.csv")

PT_acute_ori1_des2a<-fread("tracc/PT_acute_ori1_des2a.csv")
PT_acute_ori1_des2b<-fread("tracc/PT_acute_ori1_des2b.csv")

PT_acute_ori2_des2a<-fread("tracc/PT_acute_ori2_des2a.csv")
PT_acute_ori2_des2b<-fread("tracc/PT_acute_ori2_des2b.csv")

# Add in files uploaded to TRACC as TRACC gives new IDs, the analysis files need to be merged to the uploaded files to associate the correct IDs
origin1<-fread("Uploaded to tracc/Origins 1.csv")
origin2<-fread("Uploaded to tracc/Origins 2.csv")

des1<-fread("Uploaded to tracc/acute1.csv")
des2a<-fread("Uploaded to tracc/acute2a.csv")
des2b<-fread("Uploaded to tracc/acute2b.csv")

```


# CDCs merging travel time files for each mode (walk, car, PT) 

```{r}
#CDC travel time merge into one file

#car
car_cdc <-car_cdc%>% 
  rename( car_distance = TotalJourneyDistance,
    car_time = TotalJourneyTime)

#PT
PT_cdc <- PT_cdc %>% 
  rename(pt_time = TotalJourneyTime)


#merge
cdc_travel_time<-merge(car_cdc, PT_cdc, by=c('OriginId','DestinationId'), all=T,allow.cartesian=TRUE )


```

# CDCs Adding origin and destination details

```{r}

#Adding destination information
cdc_tt<- left_join(cdc_travel_time, cdc, by=c('DestinationId'='id')) %>%
  rename(destination_easting =easting, destination_northing=northing)

#Add in the eastings and northings
cdc_tt<-left_join(cdc_tt, geography[, c("id", "easting", "northing")], by=c('OriginId'='id'))

# Add travel time to postcodes
cdc_tt<- left_join(postcodes, cdc_tt,  by=c('easting','northing')) 

# Find all possible combinations
cdc2<-cdc %>%
rename(cdc_id=id, easting_cdc=easting, northing_cdc=northing)

all_cdc_combinations<-crossing(postcodes, cdc2)

# Add in travel time data
all_cdc_combinations<-left_join(all_cdc_combinations, cdc_tt[,c("pcds","ic_sitename", "car_time", "car_distance" , "pt_time")], by=c("pcds", "ic_sitename"))

all_cdc_combinations<-all_cdc_combinations%>%
  distinct()



 readr::write_csv(all_cdc_combinations, file = "cdc_tt.csv")
 

 
```

# CDCs Calculate the average travel time for each LSOA to destination

```{r}

 cdc_tt_lsoa<-all_cdc_combinations %>%
mutate(pt_time = ifelse(pt_time>60, 120, pt_time)) %>%
  mutate(car_time = ifelse(car_time>60, 120, car_time)) %>%
 mutate_all(~replace(., is.na(.), 120)) %>%
  group_by(lsoa11,ic_sitename) %>%
  summarise(car_distance=median(car_distance), 
            car_time=median(car_time), 
            pt_time=median(pt_time) )%>%
            mutate(centre="CDC")


 readr::write_csv(cdc_tt_lsoa, file = "cdc_tt_lsoa.csv")

```

# Acute Providers merging travel time files for each mode (walk, car, PT) 

```{r}
#Acute provider travel time merge into one file

#car
car_acute <-car_acute%>% 
rename( car_distance = TotalJourneyDistance,
car_time = TotalJourneyTime)

#walk
walk_acute <- walk_acute %>% 
  rename( walk_distance = TotalJourneyDistance,
    walk_time = TotalJourneyTime)


#Merging PT data for acute providers

# Ori1 Des 1
PT_acute_ori1_des1<-left_join(PT_acute_ori1_des1, origin1, by=c('OriginId'='tracc_id'))

PT_acute_ori1_des1<-left_join(PT_acute_ori1_des1, des1, by=c('DestinationId'='tracc_id'))

PT_acute_ori1_des1<-PT_acute_ori1_des1 %>%
  select(-OriginId, -DestinationId)%>%
  rename('OriginId'='V1.x','DestinationId'='V1.y')

# Ori2 Des 1
PT_acute_ori2_des1<-left_join(PT_acute_ori2_des1, origin2, by=c('OriginId'='tracc_id'))

PT_acute_ori2_des1<-left_join(PT_acute_ori2_des1, des1, by=c('DestinationId'='tracc_id'))

PT_acute_ori2_des1<-PT_acute_ori2_des1 %>%
  select(-OriginId, -DestinationId)%>%
  rename('OriginId'='V1.x','DestinationId'='V1.y')

# Ori1 Des 2a
PT_acute_ori1_des2a<-left_join(PT_acute_ori1_des2a, origin1, by=c('OriginId'='tracc_id'))

PT_acute_ori1_des2a<-left_join(PT_acute_ori1_des2a, des2a, by=c('DestinationId'='tracc_id'))

PT_acute_ori1_des2a<-PT_acute_ori1_des2a %>%
  select(-OriginId, -DestinationId)%>%
  rename('OriginId'='V1.x','DestinationId'='V1.y')

# Ori1 Des 2b
PT_acute_ori1_des2b<-left_join(PT_acute_ori1_des2b, origin1, by=c('OriginId'='tracc_id'))

PT_acute_ori1_des2b<-left_join(PT_acute_ori1_des2b, des2b, by=c('DestinationId'='tracc_id'))

PT_acute_ori1_des2b<-PT_acute_ori1_des2b %>%
  select(-OriginId, -DestinationId)%>%
  rename('OriginId'='V1.x','DestinationId'='V1.y')

# Ori2 Des 2a
PT_acute_ori2_des2a<-left_join(PT_acute_ori2_des2a, origin2, by=c('OriginId'='tracc_id'))

PT_acute_ori2_des2a<-left_join(PT_acute_ori2_des2a, des2a, by=c('DestinationId'='tracc_id'))

PT_acute_ori2_des2a<-PT_acute_ori2_des2a %>%
  select(-OriginId, -DestinationId)%>%
  rename('OriginId'='V1.x','DestinationId'='V1.y')

# Ori2 Des 2b
PT_acute_ori2_des2b<-left_join(PT_acute_ori2_des2b, origin2, by=c('OriginId'='tracc_id'))

PT_acute_ori2_des2b<-left_join(PT_acute_ori2_des2b, des2b, by=c('DestinationId'='tracc_id'))

PT_acute_ori2_des2b<-PT_acute_ori2_des2b %>%
  select(-OriginId, -DestinationId)%>%
  rename('OriginId'='V1.x','DestinationId'='V1.y')

# Merge PT into one file
PT_acute<-rbind(PT_acute_ori1_des1, 
                PT_acute_ori2_des1,
                PT_acute_ori1_des2a,
                PT_acute_ori1_des2b,
                PT_acute_ori2_des2a,
                PT_acute_ori2_des2b)

PT_acute<- PT_acute %>%
   rename(pt_time = TotalJourneyTime)%>%
  select(OriginId, DestinationId, pt_time)

#merge
acute_travel_time<-full_join(car_acute, walk_acute, by=c('OriginId','DestinationId'))

#merge
acute_travel_time<-full_join(acute_travel_time, PT_acute, by=c('OriginId','DestinationId'))

acute_travel_time<-acute_travel_time%>%
mutate(pt_time = ifelse(pt_time>60, 120, pt_time)) %>%
 mutate_all(~replace(., is.na(.), 120)) %>%
  distinct()


```

# Acute Providers Adding origin and destination details

```{r}

# Add in Destination details
acute_tt<- left_join(acute_travel_time, acute, by=c('DestinationId'='id'))%>%
  rename(destination_easting =easting, destination_northing=northing)

#Add in the eastings and northings
acute_tt<-left_join(acute_tt, geography[, c("id", "easting", "northing")], by=c('OriginId'='id'))

# Add travel time to postcodes
acute_tt<- left_join(postcodes, acute_tt, by=c('easting','northing'))%>%
  filter(!is.na(ic_sitename))

test<-acute_tt %>%
  filter(is.na(ic_sitename))

# Find all possible combinations
acute2<-acute %>%
rename(acute_id=id, easting_acute=easting, northing_acute=northing)

all_acute_combinations<-crossing(postcodes, acute2)

# Add in travel time data
all_acute_combinations<-left_join(all_acute_combinations, acute_tt[,c("pcds","ic_sitename", "car_time", "car_distance", "pt_time", "walk_time", "walk_distance")], by=c("pcds", "ic_sitename"))%>% 
  distinct()


 readr::write_csv(all_acute_combinations, file = "acute_tt.csv")
```

# Acute Providers Calculate the average travel time for each LSOA to destination

```{r}
all_acute_combinations<-read.csv("acute_tt.csv")

acute_tt_lsoa<-all_acute_combinations %>%
mutate(pt_time = ifelse(pt_time>60, 120, pt_time)) %>%
  mutate(car_time = ifelse(car_time>60, 120, car_time)) %>%
 mutate_all(~replace(., is.na(.), 120)) %>%
  group_by(lsoa11, ic_sitename, independent) %>%
  summarise(car_distance=median(car_distance), 
            car_time=median(car_time), 
            walk_distance= median(walk_distance),
            walk_time=median(walk_time),
            pt_time=median(pt_time)) %>%
            mutate(centre=ifelse(independent==1, "Private", "Acute"))

 readr::write_csv(acute_tt_lsoa, file = "acute_tt_lsoa.csv")
 

```

